Verification of concurrent design patterns with data

### 2019-02-26 2018-Arch-pNets/arch-pNets.tex
biblio compactee

%\paragraph{Operational Semantics.}
%\label{section:op-semantics}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of an open pNet is expressed as  an automaton where each transition coordinates the actions of several holes, 
the transition occurs if some predicates hold, and can involve  
 state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transition]
  \label{defn:OpenTransitions}
  An \emph{open transition} over a
  set

  \noindent
  \begin{tabular}[b]{@{}p{0.86\columnwidth}c{}@{}}
    of holes $J$ and a set of states $\mathcal{S}$ is a structure
    of the form to the right,
%
    &
%
    %% \\[-2ex]	
    %% \begin{mathpar}
    \raisebox{1mm}[0pt]{
      $\inferrule*[myfraction=\reddottedrule]
      {	\beta_j^{j\in J}, \Pred, \Post}
      {s \OTarrow {{\alpha}}s'}$
      }
    %% \end{mathpar}
%
    \\
%
    \multicolumn{2}{p{\columnwidth}}{%
%
    where $s, s'\in\mathcal{S}$;
    $\beta_j\in\actions{\variables}$ is an action of the hole
    $j$; $\alpha$ is the resulting global action; {\Pred} is a
    predicate over the different variables of the terms, labels,
    and states $\beta_j$, $s$, $\alpha$; and $\Post\in
    \assigns{\variables}$ is a set of assignments that are the
    effects of the transition.  Open transitions are identified
    modulo logical equivalence on their predicate.
%
    }
  \end{tabular}
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

>>>>

%\paragraph{Operational Semantics.}
%\label{section:op-semantics}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of an open pNet is expressed as  an automaton where each transition coordinates the actions of several holes, 
the transition occurs if some predicates hold, and can involve  
 state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transition]
  \label{defn:OpenTransitions}
  An \emph{open transition} over a
  set of holes $J$  and a set of states $\mathcal{S}$ is 
       a structure of the form:
\\[-2ex]       
       \begin{mathpar}
       \inferrule*[myfraction=\reddottedrule]
       {       \beta_j^{j\in J}, \Pred, \Post}
       {s \OTarrow {{\alpha}}s'}
       \end{mathpar}
       Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $\alpha$ is the resulting global action. \Pred\ is a predicate 
       over the different variables of the
       terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
       \assigns{\variables}$\ is 
       a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
%%   \noindent
%%   \begin{tabular}[b]{@{}p{0.86\columnwidth}c{}@{}}
%%     of holes $J$ and a set of states $\mathcal{S}$ is a structure
%%     of the form to the right,
%% %
%%     &
%% %
%%     %% \\[-2ex]	
%%     %% \begin{mathpar}
%%     \raisebox{1mm}[0pt]{
%%       $\inferrule*[myfraction=\reddottedrule]
%%       {	\beta_j^{j\in J}, \Pred, \Post}
%%       {s \OTarrow {{\alpha}}s'}$
%%       }
%%     %% \end{mathpar}
%% %
%%     \\
%% %
%%     \multicolumn{2}{p{\columnwidth}}{%
%% %
%%     where $s, s'\in\mathcal{S}$;
%%     $\beta_j\in\actions{\variables}$ is an action of the hole
%%     $j$; $\alpha$ is the resulting global action; {\Pred} is a
%%     predicate over the different variables of the terms, labels,
%%     and states $\beta_j$, $s$, $\alpha$; and $\Post\in
%%     \assigns{\variables}$ is a set of assignments that are the
%%     effects of the transition.  Open transitions are identified
%%     modulo logical equivalence on their predicate.
%% %
%%     }
%%   \end{tabular}
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}
